Integer Programming Formulations for the Shared Multicast Tree Problem

### 2018-09-05 smt/sec2-sbtsmt.tex
MI: Added a reference Halgamuge et. al. (2009), and a paragraph (2nd last paragraph in Sect. 2) that attempts to explain the difference between our energy moddel and the one in the cited paper, and why we do what we do. Label sizes of graphs increased even further

>>>>

Different energy models can be found in the literature. 
\cite{halgamuge} present a comprehensive energy model for wireless sensor networks, 
where the sources of energy consumption consist of sensing, logging, processing, transimission, actuation, transient and cluster formation.
Our energy model focuses on the energy consumed by transmission, which is also tho most energy consuming aspect of wireless networks (51\% according to \cite{halgamuge}).
Some of the measures such as sensing and cluster formation are not relevant in our model.
Another distinction is that nodes in our model are all equivalent and the data is not aggregated in the nodes.
For that reason we disregard the potential energy consumption sources occuring in sensor networks.
However, it is easy to incorporate some of the disregarded measures by adding a constant for every used Steiner node.
